A Failure Detection Approach of Data Center Networks\titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2016-06-28 SIG Proceedings Template-Jan2015 Zip/paper.tex
continue writing my paper

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
	\caption{Detection Algorithm for \textbf{Crash Decider}}
	%\label{alg0}
	\begin{algorithmic}[1]
		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
		\ENSURE $S_{i,t}$, $i$ is an imperative device

        \FOR{$i \text{ in imperative devices}$}
            \STATE $S_{i,t_0} \Leftarrow trust$
        \ENDFOR
	    \WHILE{$True$}
            \STATE $List<Integer> failsEachRack \Leftarrow \emptyset$
            \FOR{each $i$ in Servers}
                \IF{$\|CRM_{s,t_{now}}\| \geq \left\lfloor(K+1)/2\right\rfloor$}
                    \STATE $S_{i,t_{now}} \Leftarrow suspect$
                    \STATE $rackID \Leftarrow getRackID(i)$
                    \STATE $failsEachRack.get(rackID)++$
                \ELSE
                    \STATE $S_{i,t_{now}} \Leftarrow trust$
                \ENDIF
            \ENDFOR

@@

The key idea of our approach is to capture network traffic changes as times going on. If the network traffic changes significantly compared with traffic in normal conditions, we believe that there exists failures somewhere in the network. The insight is that network traffic distribution is associated with routing protocol and monitoring relationships of servers, the drastic changes of traffic probably imply failures.

@@

In order to model this data analysis problem, this paper proposes a Back Propagation Neural Network (BPNN) based classifier.

\paragraph{Feature Extraction}
The first step is to extract reasonable features from raw traffic data. To address this issue, we extract $n^2$ features, each of them denotes traffic of one direction where $n$ denotes the number of racks. Obviously, for each rack, there are $n$ different traffic directions (each one corresponds to one rack), so there are $n^2$ directions in total. Formally, the traffic feature during a time period

>>>>

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
	\caption{Detection Algorithm of \textbf{Crash Decider}}
	%\label{alg0}
	\begin{algorithmic}[1]
		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
		\ENSURE $S_{i,t}$, $i$ is an imperative device

        \FOR{$i \text{ in imperative devices}$}
            \STATE $S_{i,t_0} \Leftarrow trust$
        \ENDFOR
	    \WHILE{$True$}
            \STATE $List<Integer> failsEachRack \Leftarrow \emptyset$
            \FOR{each $i$ in Servers}
                \IF{$\|CRM_{s,t_{now}}\| \geq \left\lfloor(K+1)/2\right\rfloor$}
                    \STATE $S_{i,t_{now}} \Leftarrow suspect$
                    \STATE $rackID \Leftarrow getRackID(i)$
                    \STATE $failsEachRack.get(rackID)\text{++}$
                \ELSE
                    \STATE $S_{i,t_{now}} \Leftarrow trust$
                \ENDIF
            \ENDFOR

@@

The key idea of our approach is to capture network traffic changes over time. If the network traffic changes significantly compared with traffic in normal conditions, we believe that there exists failures somewhere in the network. The insight is that network traffic distribution is associated with routing protocol and monitoring relationships of servers, the drastic changes of traffic probably imply failures.

@@

In order to model this data analysis problem, this paper proposes a Back Propagation Neural Networks (BPNN) based method to compute failure probability of each link.

\paragraph{Feature Extraction}
The first step is to extract rational features from raw traffic data. To address this issue, we extract $v \cdot n^2$ features in total. $v$ is number of devices (CRs, ARs, ASs), each device has $n^2$ features where $n$ is the number of racks. In particular, each feature denotes traffic of one direction. Obviously, there are $n$ choices of sources and $n$ choices of destinations, so the total number of possible traffic directions is $n^2$. 
Formally, the traffic features during a time period $\Delta T$ is presented as \boldmath $x$ 
\unboldmath $=($\boldmath $x_1, x_2, ..., x_v$\unboldmath $)$, \boldmath $x_i$
\unboldmath $=(x_i^1, x_i^2, ..., x_i^{n^2})$
where $x_i^j$ stands for direction $j$ traffic of device $i$ in $\Delta T$.

\paragraph{BPNN Model}
Suppose the number of links is $e$, for each time period $\Delta T$, the output of our model should be
\boldmath $y$ 
\unboldmath $=(y_1, y_2, ..., y_e)$, where $y_i$ denotes failure probability of link $i$. We apply a BPNN model to localize the faulty link during $\Delta T$. As is shown in Figure 3, BPNN is a multi-layer perceptron architecture:
\begin{figure}
  \centering
  \includegraphics{ANN}
  \caption{Multi-layer Perceptron Architecture}
\end{figure}
To reduce the computational work of training, we only set one hidden layer, both the hidden layer neurons and output layer neurons utilize Sigmoid function as the activation function. Take the output layer as an example:
$y_i = Sigmoid(\beta_i - \theta_i)$ where $\theta_i$ is a constant term of the perceptron.

\paragraph{Training of BPNN}
To train the neural network, we apply the classical error BackPropagation (BP) algorithm \cite{rumelhart1988learning}. BP algorithm is based on gradient descent strategy.
????? % write BP algorithm?

\paragraph{The Detection Algorithm}
BPNN model is only able to identify the faulty link during one time unit, in the following part, we will introduce how we can detect multiple faults over time.

First of all, we assume that there are at most one link failure during a time unit ($\Delta T$). This assumption is partially supported by the finding proposed by Gill et. al. They find that on an average, link failures tend to be separated by a period of about one week \cite{gill2011understanding}.

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
	\caption{\textbf{Traffic Analysis Worker} Algorithm}
	\begin{algorithmic}[1]
        \REQUIRE \boldmath $x^t$ \unboldmath$=($\boldmath $x_1^t, x_2^t, ..., x_v^t$\unboldmath $)$
		\ENSURE $F_i \text{ for } i \in E$

        \STATE $\text{divide traffic data }$\boldmath $x^t$$\text{ into }$\unboldmath $t/\Delta T \text{ chunks}$

        \FOR{$i \in E$}
            \STATE $F_i \Leftarrow 0$
        \ENDFOR
        \FOR{$\text{each data chunk } $ \boldmath $x$}
        \STATE \boldmath $y$\unboldmath $\Leftarrow BPNN($\boldmath $x$\unboldmath $)$
            \FOR{$i \in E$}
                \STATE $F_i \Leftarrow F_i + y_i$
            \ENDFOR
        \ENDFOR

        \FOR{\unboldmath $i \in E$}
            \STATE $F_i \Leftarrow \frac{\Delta T F_i}{t}$
        \ENDFOR
        \STATE $\text{sort }$\boldmath $F$\unboldmath$\text{ in descending order}$
	\end{algorithmic}
\end{algorithm}

Algorithm 2 shows the algorithm of \textbf{Traffic Analysis Worker}. The input of the algorithm is the refined traffic data over time $T$. Traffic data is then divided into chunks and each chunk represents traffic data of one time unit $\Delta T$ (line 1).
